\patchcmd{\abstract}{\null\vfil}{}{}{}
\renewcommand{\abstractname}{\Large Abstract}
\begin{abstract}
    Nowadays, the volume of data throughout the world has been exponentially
    increasing and has become extremely valuable. So it is challenging for us to
    manage and exploit it. Although many advanced database management systems
    have been developed to solve this challenge, they still struggle to control
    large volumes of data. Hence, it is neccessary for us to find solutions to
    improve the performance of database management systems.

    There are many factors that affect the performance of database management
    systems, such as: cost model, cardinality estimation, memory configuration,
    excessive indexing. It is hard to focus on all of these factors to solve the
    problem. Therefore, identifying the factor that has big impact on the
    performance of database management systems plays an important role.

    This project focuses on identifying the factor which has big impact and
    showing its effect by benchmarking it in PostgreSQL and analyzing its
    effect. Besides, I also propose published solutions to reduce its effect.

    In chapter 2, I introduce the steps that a query is processed. I identify and
    show the step that affects the query performance the most. And at the end of
    this chapter, I dig deeper into this step to identify the factor that has
    big impact on query performance.

    In chapter 3, I identify common benchmarks for query performance in database
    management systems. And then i research them to find the best benchmarks for
    cardinality estimation in PostgreSQL\@. 
    
    In chapter 4, I benchmark cardinality estimation in PostgreSQL\@. Then I analyze the 			results to show the effect of cardinality estimation to query performance. Finally, I 			will propose some solutions that have been published to reduce its effect and
    improve the query performance.

    This project is made at HADAS team, LIG Laboratory under the supervision of
    Dr.\ Christophe Bobineau --- Associate Professor of Grenoble Institute of
    Technology, Maxence Ahlouche --- PhD student at Grenoble INP and Dr.\ Vu
    Tuyet Trinh --- SOICT\@.
\end{abstract}
