\renewcommand{\bibname}{REFERENCES}
\addcontentsline{toc}{chapter}{REFERENCES}
\begin{thebibliography}{9}
\bibitem{JOB}
Viktor Leis, Andrey Gubichev, Atanas Mirchev, Peter Boncz, Alfons Kemper, Thomas Neuman.
\textit{How Good Are Query Optimizers, Really?}.
Leis et al., VLBD 2015.

\bibitem{q-error}
G. Moerkotte, T. Neumann, and G. Steidl.
\textit{Preventing bad plans by bounding the impact of cardinality estimation errors.}
PVLDB, 2(1):982–993, 2009.

\bibitem{adaptive cardinality estimation}
Oleg Ivanov and Sergey Bartunov.
\textit{Adaptive cardinality estimation.}

\bibitem{neural network approach}
M. S. Lakshmi and S. Zhou.
\textit{Selectivity estimation in extensible databases - a neural network approach.}
In Proceedings of the 24rd International Conference on Very Large Data Bases, VLDB ’98, pages 623–627, San Francisco, CA, USA, 1998. Morgan Kaufmann Publishers Inc.

\bibitem{probabilistic models}
L. Getoor, B. Taskar, and D. Koller.
\textit{Selectivity estimation using probabilistic models.}
SIGMOD Rec., 30(2):461–472, May 2001.

\bibitem{sampling-based}
W. Wu, J. F. Naughton, and H. Singh.
\textit{Sampling-based query reoptimization.}
CoRR, abs/1601.05748, 2016.

\bibitem{cost models are unusable}
W. Wu, Y. Chi, S. Zhu, J. Tatemura, H. Hacigms, and J. F. Naughton.
\textit{Predicting query execution time: Are optimizer cost models really unusable?.}
In Data Engineering (ICDE), 2013 IEEE 29th International Conference on, pages 1081–1092, April 2013.

\bibitem{A multidimensional workload-aware histogram}
N. Bruno, S. Chaudhuri, and L. Gravano.
\textit{Stholes: A multidimensional workload-aware histogram, 2001.}

\bibitem{multidimensional range queries}
D. Gunopulos, V. J. Tsotras, and C. Domeniconi.
\textit{Selectivity estimators for multidimensional range queries over real attributes.}
The VLDB Journal,14:137–154, 2005.

\bibitem{SSB}
Pat O'Neil, Betty O'Neil, Xuedong Chen.
\textit{Star Schema Benchmark.}
Revision 3, June 5, 2009.
 
\bibitem{PostgreSQL internals} 
Overview of PostgreSQL Internals.
\\\texttt{https://www.postgresql.org/docs/9.6/static/overview.html} 

\bibitem{Flow of a select statement} 
Following a Select Statement Through Postgres Internals.
\\\texttt{http://patshaughnessy.net/2014/10/13/following-a-select-statement-through-postgres-internals} 

\bibitem{CE limitations} 
Cardinality Estimation Limitations.
\\\texttt{https://www.sqlpassion.at/archive/2017/05/01/cardinality-estimation-limitations} 

\bibitem{join operators} 
Introduction to Joins.
\\\texttt{https://blogs.msdn.microsoft.com/craigfr/2006/07/19/introduction-to-joins} 

\bibitem{physical operators} 
LOOP, HASH and MERGE Join Types.
\\\texttt{http://www.madeiradata.com/loop-hash-and-merge-join-types}

\bibitem{TPC} 
TPC Current Specifications.
\\\texttt{http://www.tpc.org/tpc\textunderscore documents\textunderscore current\textunderscore versions/current\textunderscore specifications.asp}
 
\end{thebibliography}